Constructing the transition graphs of interacting hysterons

### 2022-06-24 Paper_draft.tex
Finished reworking base graphs figure into Latex table & replaced figure

\usepackage[pdftex]{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage[table]{xcolor}
\newcommand\note[1]{\textcolor{red}{#1}}
\usepackage{amsmath}
\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

\newcommand\x{0.11\textwidth}

@@

\begin{figure*}[ht!]

@@

    \includegraphics[width=0.8\textwidth]{base_graphs.png}
    \caption{All possible base graphs for the two- and three-hysteron systems. a) All base graphs for $N=2$; since scrambling is not possible for $N=2$, the base graphs are the two Preisach graphs. b) All Preisach (top) and scrambled (bottom) base graphs for $N=3$. Graphs on a gray background are possible for general, but not linear coupling.}
\end{figure*}

@@

@@

In a scrambled graph, one or more of the transitions in the graph deviates from the main loop, so that each main loop corresponds to a number of base graphs (Fig.\ref{fig:basegraphs_n3}).\\

>>>>

\usepackage[pdftex]{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage[table]{xcolor}
\newcommand\note[1]{\textcolor{red}{#1}}
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

\newcommand\x{0.11\textwidth}
\newcommand\y{0.5\textwidth}

@@

\begin{minipage}{0.6\textwidth}
\textbf{a)}\\

@@

\begin{tabular}{|c|c|}
\textbf{(1, 2)}&\textbf{(2, 1)}\\ \hline
  \includegraphics[width=\y]{24-06-2022_N2graphs_preisach/graph0.pdf}
& \includegraphics[width=\y]{24-06-2022_N2graphs_preisach/graph1.pdf} \\ \hline
\end{minipage}
\begin{minipage}{0.95\textwidth}
\textbf{b)}\\

@@

\end{minipage}
\caption{All possible base graphs for the two- and three-hysteron systems, indexed per main loop. a) All base graphs for $N=2$; since scrambling is not possible for $N=2$, the base graphs are the two Preisach graphs. b) All Preisach (top) and scrambled (bottom) base graphs for $N=3$. Graphs on a gray background are possible for general, but not linear coupling.}

@@

In a scrambled graph, one or more of the transitions in the graph deviates from the main loop, so that each main loop corresponds to a number of base graphs (Table.\ref{fig:basegraphs_n3}).\\
